Analysing Constraint Grammar with a SAT solver

### 2015-10-19 paper/lrec/lrec2016_listenmaa_claessen.tex
more stuff to table

\newcommand{\mainfontfamily}{Palatino}
\setmainfont[
  Ligatures=TeX,
  Scale=0.95,
]{\mainfontfamily}
% \newfontfamily\scshape[Letters=SmallCaps, Numbers=Uppercase] % {Myriad Pro} % {TeX Gyre Pagella}

@@

\begin{abstract}
We describe a method for analysing Constraint Grammar by encoding it
as a SAT problem.
Our tools can detect internal conflicts or redundancies in a grammar,
as well as generate example sequences to demonstrate the effect of some rule or rule set.
No corpus is required, only a morphological lexicon.
%We test our tools with grammars from 100-1000 rules.
\end{abstract}

\begin{table*}[]
\centering
\begin{tabular}{|l|l|l|l|}
\hline
\textbf{Word} & \textbf{Variables}                                                          & \textbf{Default rules}               & \textbf{Constraint rules}                                  \\ \hline
``the''         & \texttt{the\_det}                                                           & \texttt{the\_det}                    & \multirow{2}{*}{\texttt{the\_det}  $\Rightarrow$ $\neg$\texttt{bear\_v\_pl}} \\ \cline{1-3}
``bear''        & \begin{tabular}[c]{@{}l@{}}\texttt{bear\_n\_sg} \\ \texttt{bear\_v\_pl}\end{tabular} & \texttt{bear\_n\_sg} $\vee$ \texttt{bear\_v\_pl} &                                                            \\ \hline
\end{tabular}
\caption{SAT-encoding of \texttt{REMOVE v IF (-1 det)} applied to \emph{the bear}}
\label{table:vars}
\end{table*}

>>>>

\newcommand{\mainfontfamily}{Palatino}
\setmainfont[
  Ligatures=TeX,
  Scale=0.95,
]{\mainfontfamily}
%\newfontfamily\scshape[Letters=SmallCaps, Numbers=Uppercase] % {Myriad Pro} % {TeX Gyre Pagella}

@@

\begin{abstract}
We describe a method for analysing Constraint Grammar by encoding it
as a SAT problem.
Our tools can detect internal conflicts or redundancies in a grammar,
as well as generate examples to demonstrate the effect of some rule or rule set.
No corpus is required, only a morphological lexicon.
%We test our tools with grammars from 100-1000 rules.
\end{abstract}

\begin{table*}[]
\centering
\begin{tabular}{|l|l|l|l|}
\hline

\textbf{Analyses}                                                                                                 & \textbf{Variables}                                                          & \textbf{Default rules}                                    & \textbf{Constraint rules}                                                          \\ \hline
\multicolumn{1}{|l|}{\begin{tabular}[c]{@{}l@{}}``\textless{}the\textgreater''\\$\qquad\quad$"the" det\end{tabular}}     & \multicolumn{1}{l|}{\texttt{the\_det}}                                      & \multicolumn{1}{l|}{\texttt{the\_det}}                    & \multicolumn{1}{l|}{\multirow{2}{*}{\texttt{the\_det $\Rightarrow$ $\neg$bear\_v\_pl}}} \\ \cline{1-3}
\begin{tabular}[c]{@{}l@{}}"\textless{}bear\textgreater"\\$\qquad\quad$"bear" n sg\\$\qquad\quad$"bear" v pl\end{tabular} & \texttt{\begin{tabular}[c]{@{}l@{}}bear\_n\_sg \\ bear\_v\_pl\end{tabular}} & \multicolumn{1}{l|}{\texttt{bear\_n\_sg $\vee$ bear\_v\_pl}} & \multicolumn{1}{l|}{}                                                              \\ \hline
\end{tabular}
\caption{SAT-encoding of \texttt{REMOVE v IF (-1 det)} applied to \emph{the bear}}
\label{table:vars}
\end{table*}
